Windowed least-squares model reduction for dynamical systems

### 2019-10-07 section3/space_time.tex
latest

\subsection{\spaceTimeAcronym\ trial spaces}
\KTC{Error in first equation. This is the approximate solution not the real
one. Use parallel language to hwo this was done in the last section for
S-reduction trial subspaces. Also make sure the basis is zero at the beginning
of the interval and the affine transformation is taken to be the solution at
the end of the last window. This will not be too trivial, as the solution on
the previous slab enters the trial subspace definition.}

We now briefly consider \spaceTimeAcronym\ trial subspaces. 
The \spaceTimeAcronym\ trial subspace over the $n$th time window approximates
the FOM ODE solution trajectory $\stateFOM\in\RR{N}\otimes\timeSpace$
with $\approxstateArgnt{n} \in \stspaceSTArg{n}$, where
\begin{equation}\label{eq:st_sttrialspace}
 \stspaceSTArg{n} \defeq
 \Range{\stbasisArgnt{n}} + \stateInterceptArg{n}\otimes \onesFunctionArg{n} .
\end{equation}
Here $\stbasisArgnt{n} \in \RR{\fomdim \times \stdimArg{n}} \otimes \timeSpaceArg{n}$, $n=1,\ldots,\nslabs$, with $\stbasisArgnt{n}: \timeDummy \mapsto \stbasisArgnt{n}(\timeDummy)$ and $\stbasisArg{n}{0} = \bz$ is the space--time trial basis matrix \textit{function}. At any time instance $t \in [\timeStartArg{n},\timeEndArg{n}]$, the \spaceTimeAcronym\ trial subspace approximates the FOM ODE solution as,
 \begin{equation}\label{eq:stapprox}
 \stateFOMArg{n}{t} \approx \approxstateArg{n}{t}  = \stbasisArg{n}{t} \stgenstateArg{n} + \stateInterceptArg{n},
\end{equation}
where $\stgenstateArg{n} \in \RR{\stdimArg{n}}$ are the space--time generalized coordinates over the $n$th window.

>>>>

\subsection{\spaceTimeAcronym\ trial spaces}\label{sec:wls_spacetime}
\KTC{Error in first equation. This is the approximate solution not the real
one. Use parallel language to hwo this was done in the last section for
S-reduction trial subspaces. Also make sure the basis is zero at the beginning
of the interval and the affine transformation is taken to be the solution at
the end of the last window. This will not be too trivial, as the solution on
the previous slab enters the trial subspace definition.}

We now briefly consider \spaceTimeAcronym\ trial subspaces. 
The \spaceTimeAcronym\ trial subspace over the $n$th time window approximates
the FOM ODE solution trajectory $\stateFOM\in\RR{N}\otimes\timeSpace$
with $\approxstateArgnt{n} \in \stspaceSTArg{n}$, where
\begin{equation}\label{eq:st_sttrialspace}
 \stspaceSTArg{n} \defeq
 \Range{\stbasisArgnt{n}} + \stateInterceptArg{n}\otimes \onesFunctionArg{n} .
\end{equation}
Here $\stbasisArg{n}{t} \in \RR{\fomdim \times \stdimArg{n}}$, $n=1,\ldots,\nslabs$, with $\stbasisArgnt{n}: \timeDummy \mapsto \stbasisArgnt{n}(\timeDummy)$ and $\stbasisArg{n}{0} = \bz$ is the space--time trial basis matrix \textit{function}. At any time instance $t \in [\timeStartArg{n},\timeEndArg{n}]$, the \spaceTimeAcronym\ trial subspace approximates the FOM ODE solution as,
 \begin{equation}\label{eq:stapprox}
 \stateFOMArg{n}{t} \approx \approxstateArg{n}{t}  = \stbasisArg{n}{t} \stgenstateArg{n} + \stateInterceptArg{n},
\end{equation}
where $\stgenstateArg{n} \in \RR{\stdimArg{n}}$ are the space--time generalized coordinates over the $n$th window.

### 2019-10-07 section3/tclsrm_formulation.tex
latest

\subsection{\methodAcronym\ summary}
This section outlined the \methodAcronym\ method for model reduction. In summary, \methodAcronym\ sequentially minimizes the time continuous FOM ODE residual over the range of a space--time trial subspace for a series of time windows: \methodAcronym\  
\KTC{Here, use the same language as earlier regarding sequential computation
of these coordinates that satisfy...} computes the generalized coordinates
$\genstateArgnt{n}$, for $n = 1,\ldots,\nslabs$, as the solution to the
minimization problems, \KTC{remove superscript from optimizaton variable
everywhere}
\begin{equation*}
\underset{\stateyArgnt{n} \in \stspace^n}{\text{minimize } }
\mathcal{J}^n(\stateyArgnt{n}), \qquad n = 1,2,...,\nslabs,
\end{equation*}
\KTC{Everywhere in the manuscript, eliminate $1,2,\ldots,n$. Make this 
$1,\ldots,n$. Also, above you use three dots instead of ldots. Fix this
everywhere}
where,
\begin{align*}
\mathcal{J}^n &\vcentcolon \statey \mapsto
\frac{1}{2} \int_{\timeStartArg{n}}^{\timeEndArg{n}} \big[ \dot{\statey}(t)
- \velocity(\stateyArg{}{t},t) \big]^T \stweightingMatArg{n} \big[
\dot{\statey}(t) - \velocity(\stateyArg{}{t},t) \big] d t \\
&\vcentcolon \RR{\fomdim}\otimes \timeSpaceArg{n} \rightarrow
\RR{},
\end{align*}
subject to the boundary and continuity conditions. For the \spatialAcronym\ trial subspaces, the stationary conditions for the residual minimization problem can be derived via the Euler--Lagrange equations and yield the system over the $n$th window for $t \in [\timeStartArg{n},\timeEndArg{n}]$,
\begin{align*}\
&\mass \frac{d}{dt} \genstateArg{n}{t}  -  \basisspace^T
\stweightingMatArgt{n}{t} \velocity(\veloargsromn) =  \mass \adjointArg{n}{t} , \\
 &\mass \frac{d}{dt} \adjointArg{n}{t}  + \basisspace^T \bigg[\frac{\partial
\velocity}{\partial \statey} (\veloargsromn) \bigg]^T \stweightingMatArgt{n}{t} \basisspace
 \adjointArg{n}{t} = \nonumber \\ 
&-\basisspace^T \big[
\frac{\partial \velocity}{\partial \statey}(\veloargsromn) \big]^T \stweightingMatArgt{n}{t} \bigg( \mathbf{I} -
\basisspace [\massArgt{n}{t}]^{-1} \basisspace^T \stweightingMatArgt{n}{t} \bigg)
 \bigg( \basisspace \frac{d}{dt}\genstateArg{n}{t}  -
\velocity(\veloargsromn) \bigg),  &
%\genstateArg{n}{\timeStartArg{n}} = \begin{cases}
%\genstate^{n-1}(\timeEndArg{n-1}) & n=2,\ldots,\nslabs, \\
%\basisspace^T(\approxstate_0 - \stateIntercept) & n=1, \end{cases}\\ &
%\adjointArg{n}{\timeEndArg{n}} = \boldsymbol 0.
\end{align*} 
\KTC{use en-dash here to separate numbers} subject to the boundary conditions~\eqref{eq:lspg_bcs1}-\eqref{eq:lspg_bcs}. The Euler-Lagrange equations expose the fact that, for \spatialAcronym\
trial subspaces, \methodAcronym\ can be alternatively interpreted as a Lagrange problem from optimal control: the Galerkin method is forced by a 
controller that enforces the residual minimization property.

\KTC{Passive voice:} \spaceTimeAcronym\ trial subspaces were additionally considered. For \spaceTimeAcronym\ trial subspaces, in where the generalized coordinates are no longer functions, the stationary conditions correspond to an algebraic system of equations.

>>>>

\subsection{\methodAcronym\ summary}
This section outlined the \methodAcronym\ method for model reduction. In summary, \methodAcronym\ sequentially minimizes the time continuous FOM ODE residual over the range of a space--time trial subspace for a series of time windows: \methodAcronym\  
\KTC{Here, use the same language as earlier regarding sequential computation
of these coordinates that satisfy...} computes the generalized coordinates
$\genstateArgnt{n}$, for $n = 1,\ldots,\nslabs$, as the solution to the
minimization problems, \KTC{remove superscript from optimizaton variable
everywhere}
\begin{equation*}
\underset{\stateyArgnt{} \in \stspace^n}{\text{minimize } }
\mathcal{J}^n(\stateyArgnt{}), \qquad n = 1,\ldots,\nslabs,
\end{equation*}
where,
\begin{align*}
\mathcal{J}^n &\vcentcolon \statey \mapsto
\frac{1}{2} \int_{\timeStartArg{n}}^{\timeEndArg{n}} \big[ \dot{\statey}(t)
- \velocity(\stateyArg{}{t},t) \big]^T \stweightingMatArg{n} \big[
\dot{\statey}(t) - \velocity(\stateyArg{}{t},t) \big] d t \\
&\vcentcolon \RR{\fomdim}\otimes \timeSpaceArg{n} \rightarrow
\RR{},
\end{align*}
subject to the boundary and continuity conditions. For the \spatialAcronym\ trial subspaces, the stationary conditions for the residual minimization problem can be derived via the Euler--Lagrange equations and yield the system over the $n$th window for $t \in [\timeStartArg{n},\timeEndArg{n}]$,
\begin{align*}\
&\massArg{n}  \genstateDotArg{n}{t}  -  \basisspaceTArg{n}
\stweightingMatArgt{n}{t} \velocity(\veloargsromn) =  \massArg{n} \adjointArg{n}{t} , \\
 &\massArg{n} \adjointDotArg{n}{t}  + \basisspaceTArg{n} \bigg[\frac{\partial
\velocity}{\partial \statey} (\veloargsromn) \bigg]^T \stweightingMatArgt{n}{t} \basisspaceArg{n}
 \adjointArg{n}{t} = \nonumber \\ 
&-\basisspaceTArg{n} \big[
\frac{\partial \velocity}{\partial \statey}(\veloargsromn) \big]^T \stweightingMatArgt{n}{t} \bigg( \mathbf{I} -
\basisspaceArg{n} [\massArg{n}]^{-1} \basisspaceTArg{n} \stweightingMatArgt{n}{t} \bigg)
 \bigg( \basisspace \genstateDotArg{n}{t}  -
\velocity(\veloargsromn) \bigg),  &
%\genstateArg{n}{\timeStartArg{n}} = \begin{cases}
%\genstate^{n-1}(\timeEndArg{n-1}) & n=2,\ldots,\nslabs, \\
%\basisspace^T(\approxstate_0 - \stateIntercept) & n=1, \end{cases}\\ &
%\adjointArg{n}{\timeEndArg{n}} = \boldsymbol 0.
\end{align*} 
subject to the boundary conditions~\eqref{eq:lspg_bcs1}--\eqref{eq:lspg_bcs}. The Euler-Lagrange equations expose the fact that, for \spatialAcronym\
trial subspaces, \methodAcronym\ can be alternatively interpreted as a Lagrange problem from optimal control: the Galerkin method is forced by a 
controller that enforces the residual minimization property.

Section~\ref{sec:wls_spacetime} additionally considered \spaceTimeAcronym\ trial subspaces. For \spaceTimeAcronym\ trial subspaces, in where the generalized coordinates are no longer functions, the stationary conditions correspond to an algebraic system of equations.
